### 2016-02-12 mcmc.tex
clarification

\begin{problem}
Modify the sampler you wrote in \problemname~\ref{prob:MH} to take
steps not in $x$ but in $\ln x$.  That is, replace the Gaussian
proposal distribution $q(x'\given x)$ with a Gaussian distribution in
$\ln x$ $q(\ln x'\given \ln x)$.  What about your answers change?  How
wrong is your answer?  Bonus points: Compute the analytic function
that you have sampled from (that is, not $p(x)$) and over-plot it on
your histogram.
\end{problem}

>>>>

\begin{problem}
Modify the sampler you wrote in \problemname~\ref{prob:MH} to take
steps not in $x$ but in $\ln x$.  That is, replace the Gaussian
proposal distribution $q(x'\given x)$ with a Gaussian distribution in
$\ln x$ $q(\ln x'\given \ln x)$, but---incorrectly---make no other
changes.  What about your answers change?  How wrong is your answer?
Bonus points: Compute the analytic function that you have sampled from
(that is, not $p(x)$) and over-plot it on your histogram.
\end{problem}
